\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Rodrigo Emídio} \\ \vspace{5pt}
    \small \href{tel:+351929037362}{\raisebox{-0.1\height}\faPhone\ {+351929037362}} ~ \href{mailto:rodrigo.castro.emidio@gmail.com}{\raisebox{-0.2\height}\faEnvelope\ {rodrigo.castro.emidio@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/rodrigo-emídio/}{\raisebox{-0.2\height}\faLinkedin\ {linkedin.com/in/rodrigo-emídio}}  ~
    \href{https://github.com/rodrigoemidiodev}{\raisebox{-0.2\height}\faGithub\ {github.com/rodrigoemidiodev}}
    \vspace{-8pt}
\end{center}

%-----------ABOUT ME------------
\section{About Me}
    \text{My name is Rodrigo Emídio, and I am a graduated student in Computer Science at University of Porto. My main fields of interest are Data Science, Web Development and Algorithms. In my free time, I enjoy watching TV shows, hanging out with friends and playing video games.}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Faculty of Sciences of the University of Porto}{Sep 2020 -- June 2024}
      {Bachelor of Computer Science}{Porto, Portugal}
  \resumeSubHeadingListEnd

%-----------PROFESSIONAL EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {INESC TEC}{Oct 2022 -- Jan 2023}
      {Front-End Developer Intern}{Porto, Portugal}
      \resumeItemListStart
        \resumeItem{Developed the front-end of a cross-platform mobile application using the Ionic framework.}
        \resumeItem{Used the INESC TEC API to make HTTP requests with user inputted data.}
        \resumeItem{Used Git to organize modifications.}
        \resumeItem{Utilized Capacitor to deploy and test in real time the application on Android.}
    \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-16pt}

%----------VOLUNTEER EXPERIENCE----------
\section{Volunteer Experience}
    \resumeSubHeadingListStart
        \resumeSubheading{NUCC-FCUP}{Oct 2021 -- Present}{Pedagogical Department Coordinator / Treasurer}{Faculty of Sciences of the University of Porto}
            \resumeItemListStart
                \resumeItem{Organized formal activities undertaken by the student nucleus such as workshops and lectures, which helped me develop leadership and work management skills.}
                \resumeItem{Managed the nucleus' accounting, which helped me increase my knowledge in the finantial field and hone my leadership capacity.}
            \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{University Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Parliament Database} $|$ \emph{SQL, Python}}{Nov 2021 -- Dec 2021}
          \resumeItemListStart
            \resumeItem{Modeled a database to store data related to a fictitious version of the Portuguese Parliament.}
            \resumeItem{Utilized Flask and PyMySQL libraries to build a web app that interfaces with the developed SQL database.}
          \resumeItemListEnd
          \vspace{-13pt}
          \resumeProjectHeading
          {\textbf{Pascal-0 Compiler} $|$ \emph{Haskell}}{Nov 2022 -- Dec 2022}
          \resumeItemListStart
            \resumeItem{Developed a compiler for a subset of Pascal, that reads source code and generates the corresponding MIPS assembly code.}
            \resumeItem{Used Alex to generate the Lexer and Happy to generate the Parser.}
          \resumeItemListEnd
          \vspace{-13pt}
          \resumeProjectHeading
          {\textbf{The Nim Game} $|$ \emph{HTML/CSS, JavaScript}}{Oct 2022 -- Dec 2022}
          \resumeItemListStart
            \resumeItem{Developed a web version of the Nim Game.}
            \resumeItem{Front-end implementation of a single-page application.}
            \resumeItem{Implemented a Node server and configured HTTP requests to allow players from different machines play together.}
          \resumeItemListEnd
          \vspace{-13pt}
          \resumeProjectHeading
          {\textbf{Classification Algorithms Performance} $|$ \emph{Python}}{Mar 2023 -- May 2023}
          \resumeItemListStart
            \resumeItem{Measured the performance impact of a classification algorithm by changing its preference criterion.}
          \resumeItemListEnd
          \vspace{-13pt}
          \resumeProjectHeading
          {\textbf{Concurrent Sets} $|$ \emph{Java}}{May 2023 -- Jun 2023}
          \resumeItemListStart
            \resumeItem{Concurrent implementation of sets based on hash sets.}
            \resumeItem{Used concurrency techniques such as synchronized blocks, atomic operations, and various types of locks to assure mutual exclusion and guarantee smooth read-write operations.}
            \resumeItem{Used STM to simplify concurrency operations.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}


%
%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Technologies}{: C, C++, Excel, Git, HTML/CSS, Haskell, Java, JavaScript, Linux, \LaTeX, Markdown, Python, React, SQL} \\
     \textbf{Communication}{: Portuguese (Native), English (B2), Spanish (B1)}
    }}
 \end{itemize}
 \vspace{-16pt}

\end{document}
